Kelp morphometric properties and the link to hydrodynamic modelling

### 2018-10-16 proposal_draft_2018.Rmd
house cleaning

---
title: "Kelp morphometric properties and the link to hydrodynamic modelling"
author:
- affiliation: University of the Western Cape
  name: Ross Coppin, AJ Smit, Christo Rautenbach
date: "2018"
output:
  word_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    highlight: zenburn
    toc: yes
  pdf_document:
    toc: yes
    toc_depth: 4
bibliography: LaTeX/mycollection.bib   
---

>>>>

---
title: "Kelp morphometric properties and the link to hydrodynamic modelling"
author:
- affiliation: University of the Western Cape
  name: Ross Coppin, AJ Smit, Christo Rautenbach
date: "2018"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
  word_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    highlight: zenburn
    toc: yes
bibliography: LaTeX/mycollection.bib   
---
